Data Preparation

### 2019-01-09 Data Preparation.Rmd
Saving data for other scripts
Footnotes

>>>>

```{r}
save(lists, d_course, d_AoD, d_assessment, d_transcript,
     file = "data_pillar_1.RDATA")
save(lists, d_course, d_AoD, d_assessment, d_transcript,
     d_overview_stem, d_description_stem,
     file = "data_pillar_2.RDATA")
```

[^1]: We do not include all assessments and all AoDs on the plots in order to keep them readable.

[^2]: We are currently cleaning the dataset containing the transcripts of all the students of the college (alumni and current students) in order to integrate it to the analysis.
